A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-06-28 paper.tex
Move some MAM description to Chap 4 & add figures

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

@@

A. Colman et al. \cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by linking the messages to a list. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} is a smart transportation system. The authors offer a key and entry point management with MAM that minimize the information that data producers need to hold. Also, the trading procedure is automated and enforced with Ethereum smart contracts. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading are not illustrated in this paper.

Researches below adopt MAM as data storage and transmit data with it as well. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation, targets for IoT data streams trading. Data streams are stored via MAM and paid in IOTA. Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace. O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node (SN) system to exchange data and establish a data monetization economy paradigm. The Back-End server helps SNs to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to it's quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy is rather simple, which do not take subscription based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized which does not exist any intermediate server but data providers only, data providers attach and trade data streams via MAM, and specific tags are added in transaction as an index for different usages, such as payment check and product information search. However, once the data amount grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and to prevent adversaries spamming transactions.

@@

\section{System Design Thinking}
\subsection{Data trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:system_design}.

@@

% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\begin{itemize}
    \item \textbf{Scalability}: for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \item \textbf{Integrity}: 
	\begin{itemize}    	
    	\item messages published to DLT are tamperproof that against malicious modification. 
    	\item messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}    	
    	\item The encrypted data are uploaded that only participants that have keys can decrypt. 
    	\item The authorized users can retrieve data streams, since data is written on DLT which can be queried as long as the IOTA network is alive.
    	\item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

% alternative solution => IPFS(data) + MAM(index)

@@

>>>>

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

@@

\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint. \cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement. This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.

The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading. Data streams are stored via MAM and data payment is paid in IOTA. Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace. In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well. The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.

\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS. Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract. Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach. Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions. Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from. Also, the details of trading are not illustrated in this paper.

@@

\section{System Design Thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{pub_sub_model}
    \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams.

@@

\begin{itemize}
    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \item \textbf{Integrity}: 
	\begin{itemize}    	
    	\item Messages published to the Tangle are tamperproof that against malicious modification. 
    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}    	
    	\item The encrypted data are uploaded that only participants that have keys can decrypt. 
    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
    	\item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

MAM publishes authenticated streaming data to channel and endpoint as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control. The payload of a MAM message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents, the ciphertext is then signed with \textbf{signature key} generated with MSS and attached to the Tangle. This approach allows users to validate the signatures without knowing the actual contents but ensuring the messages do come from the exact source. See Fig.~\ref{fig:channel_and_key} for illustration. Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure*}

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\section{Masked Authenticate Messaging}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored. One can easily prove himself by sharing the identifier on MAM without any authority.
